### 2020-05-01 thesis_template/3_Body/model/knn.tex
knn result

\subsection{Result}
\label{sec:history}

@@

>>>>

\subsection{Result}
\label{sec:history}
Figure~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
The algorithms whose runtime is showing 0 seconds are algorithms that are terminated during execution due to fail of memory allocation.
The algorithm with 2 batches, strategy 1, Arc method, and 20K and 25K dimension, 
and the algorithm with 2 batches, strategy 1, deep-copy method, 25K dimension are such algorithms whose memory capacity get over during execution time.

As shown in Figure~\ref{fig:preprocess}, the algorithms using Arc is much slower than using deep-copy in preprocessing phase. 
If we set algorithm's parameter in 3 batches , strategy 2, and 25K dimension, the algorithm with Arc is about 38\% slower than the one with deep-copy. 
In addition, the algorithms with strategy 2 are slower than with strategy 1. When the parameters are set in 3 batches, deep-copy method, and 25K dimension, 
runtime performance of the algorithm with strategy 2 is about 85\% slower than one with strategy 1. 
Furthermore, as we increase the number of dimension, the number of batch becomes more and more critical to runtime performance of the algorithms with deep-copy.
The runtime differences among different number of batch are about 44\%, 28\%, and 39\% for the algorithms whose parameters are set in strategy 2 and Arc method. 
However, those for the algorithms with strategy 2 and deep-copy method are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimension.

@@

\subsection{Discussion}
\label{sec:history}
